
\section{Education}\label{education}

\begin{itemize}
\tightlist
\item
  Graduate: \textbf{Carnegie Mellon University}, Pittsburgh, PA
  \hfill (Aug 2017 - Present)

  \begin{itemize}
  \tightlist
  \item
    Master of Science in Intelligent Information Systems
  \end{itemize}
\item
  Undergraduate: \textbf{Nanyang Technological University}, Singapore
  \hfill (Aug 2010 -- Jun 2014)

  \begin{itemize}
  \tightlist
  \item
    Bachelor of Engineering (Honours) in Computer Science with a GPA of
    \textbf{4.78/5}.
  \item
    Specialization in Intelligent Systems, Minor in Business.
  \item
    \textbf{Dean's List} - Academic Year 2012-13, Academic Year 2013-14
  \item
    Awarded President's Research Scholarship - offered to the top 5\% of
    the cohort - Academic Year 2011-12
  \item
    Awarded full scholarship for university education.
  \end{itemize}
\item
  High School: \textbf{St.~James' School}, Kolkata, India
  \hfill (Graduated in May 2010)
\end{itemize}

\section{Employment History}\label{employment-history}

\begin{itemize}
\tightlist
\item
  \textbf{Zendesk, Inc.} - \emph{Senior Software Engineer, Zendesk Chat
  (Backend/Platform)}, Singapore \hfill (Jul 2016 - Aug 2017)
\item
  \textbf{Zendesk, Inc.} - \emph{Software Engineer, Zendesk Chat
  (Backend/Platform)}, Singapore \hfill (Jul 2014 - Jul 2016)

  \begin{itemize}
  \tightlist
  \item
    \emph{Engineering Lead} for the internal \textbf{push-notification
    microservice}: Re-wrote session management logic, architected new
    systems and infrastructure to support robust push notification
    delivery.
  \item
    \emph{Engineering Lead} for the internal microservice for
    \textbf{feature entitlement}, gating and staggered rollout.
  \item
    \emph{Engineering Lead} for \textbf{billing integration} with the
    shared billing service, replacing legacy systems, and mass migrating
    customers to the new system.
  \item
    \emph{\href{https://developer.zendesk.com/rest_api/docs/chat/introduction}{Public
    Rest API}} - Worked on v1.0 of the Zendesk Chat public REST API.

    \begin{itemize}
    \tightlist
    \item
      Wrote the view transformation layer to transform internal data
      models into publicly consumable data,
    \item
      Developed internal structure for authorization checks
    \end{itemize}
  \item
    \emph{Live Chat Servers} - Worked on various iterations of the
    application that powers live chat, working on features like REST API
    for ongoing chats, support for concurrent sessions, low-level
    protocol enhancements etc.
  \item
    \emph{Event Framework} - Wrote the event framework that produces
    product-wide events to Kafka. Some were piped via a pool of Logstash
    servers depending on importance and volume.
  \item
    \emph{Webhooks} - Developed delivery and retry mechanism for payload
    delivery.
  \item
    \emph{Test Framework} - Made several improvements to the unit test
    suite: improvements to the test suite lifecycle, increased coverage
    and heavily reduced suite runtimes with micro-optimizations.
  \item
    \emph{Miscellanous Responsibilites} - Development environments,
    staging servers, CI setup, hiring, mentoring, etc.\\
    \emph{Technologies Used} - Python, Django, Flask, Celery, Nose,
    JavaScript, Node, Redis \& Redis Cluster, Memcached, Kafka,
    Logstash, MySQL, Docker, etc.
  \end{itemize}
\item
  \textbf{IBM Corporation} - \emph{Software Engineering Intern},
  Singapore \hfill (May 2013 - Aug 2013)
\item
  \textbf{IBM Corporation} - \emph{Software Engineering Intern},
  Singapore \hfill (Jun 2012 - Dec 2012)

  \begin{itemize}
  \tightlist
  \item
    Developed core components for a mobile port of IBM Security Access
    Manager for Enterprise Single Sign-On,
    \href{https://itunes.apple.com/us/app/isam-essom/id741972716?mt=8}{ISAM-ESSOm},
    for providing single sign-on capabilities on the iOS platform.
  \item
    Built the fully-featured, UIWebView-based embedded browser which
    provides single sign-on capabilities.
  \end{itemize}
\end{itemize}

\section{Open Source Contributions
(Selected)}\label{open-source-contributions-selected}

\begin{itemize}
\tightlist
\item
  \href{https://github.com/twitter/twitter-cldr-js}{\textbf{TwitterCLDR}}
  - Regular contributor to Twitter's open source JavaScript
  implementation of the ICU (International Components for Unicode) that
  uses the Common Locale Data Repository to format dates, plurals, and
  more. Implemented features such as Text Segmentation, Unicode Regex
  Parser, Rule-based number formatting etc.
\item
  \href{https://github.com/getsentry/raven-python}{\textbf{raven-python}}
  - Added support for capture-sampling per message. Added support for
  logging filters, and exclusions when used with Flask.
\item
  \href{https://github.com/zopim/txconnpool}{\textbf{txconnpool}} -
  Added support to create a connection pool to a pool of servers rather
  than just 1.
\item
  \href{https://github.com/zopim/blinker}{\textbf{blinker}} - Added
  support for sending signals without propagating resulting exceptions
  and support for connecting via multiple objects in a single decorator.
\end{itemize}

\section{Other Projects (Selected)}\label{other-projects-selected}

\begin{itemize}
\item
  \textbf{Virtual Interaction with Physical Objects Using Kinect and
  iPhone} - \emph{Final Year Project} - Interfacing a Kinect, an iPhone,
  and a projector with a central server to process motion to demonstrate
  virtual interaction with real objects.
\item
  \href{https://github.com/arnavk/FacebookSearch}{\textbf{Facebook
  Search}} - \emph{Information Retrieval} -
  \href{http://facebook-search.herokuapp.com/}{App} to perform full text
  search on a user's post history.
\item
  \href{https://github.com/arnavk/Twitter-Visualiser}{\textbf{Twitter
  Visualizer}} - \emph{Data Mining} - App to generate a timeline for the
  worldwide flow of hashtags and track local trends.
\item
  \href{https://github.com/arnavk/NLP}{\textbf{Twitter Summarizer}} -
  \emph{NLP} - An app to summarise information on a topic by extracting
  descriptive phrases from tweets.
\item
  \href{https://itunes.apple.com/us/app/dbauggle!/id625981185?mt=8}{\textbf{dBauggle}}
  - \emph{Software Engineering} - iOS word-game for children with
  special needs, built with cocos2d.
\item
  \href{https://github.com/arnavk/Pebble-MusicTweeter}{\textbf{Pebble
  Music Tweeter}} - \emph{Hobby} - Pebble Watchapp + companion iOS app
  using the Twitter API and Pebble SDK to Tweet the currently playing
  music from the smartwatch.
\end{itemize}

\section{Technical Skills}\label{technical-skills}

\begin{itemize}
\tightlist
\item
  Languages: Comptetent: Python. Can get by: Javascript, CoffeeScript,
  Java, Objective-C, and others.
\item
  Technologies (miscellaneous): Django, Flask, Celery, Nose, Node,
  Jasmine, Redis, Redis Cluster, Memcached, MySQL, Kafka, Docker,
  Logstash etc.
\item
  Represented NTU in International Collegiate Programming Competition
  (ACM-ICPC) Regionals, Kuala Lumpur (2011).
\end{itemize}

\section{Extra-Curricular Activities
(University)}\label{extra-curricular-activities-university}

\begin{itemize}
\tightlist
\item
  \textbf{NTU Open Source Society} \hfill (Aug 2010 - May 2014)

  \begin{itemize}
  \tightlist
  \item
    \textbf{President} in AY2012-13, \textbf{Vice-President} in
    AY2011-12
  \item
    Headed the management committee of the resident hacker-club that
    hosted weekly workshops, recruitment events and promoted technology
    on the campus.
  \item
    Organised various workshops (\& presented a few), recruitments
    events and Ubuntu release parties.
  \end{itemize}
\item
  \textbf{IT \& Media Officer - Computer Engineering Club}
  (\textbf{Students' Council}) \hfill (Sept 2012 - Aug 2013)

  \begin{itemize}
  \tightlist
  \item
    Steered the annual branding initiative, produced and redesigned the
    School's publication and organised the school's first Hackathon.
    (AY2012-13)
  \end{itemize}
\item
  \textbf{Layout Editor - The Tribune}, Official Campus Newspaper
  \hfill (Sept 2011 - Aug 2012)

  \begin{itemize}
  \tightlist
  \item
    Led a rebranding initiative and major redesign of the newspaper,
    leading to 2x increase in readership and distribution.
  \end{itemize}
\end{itemize}

\section{Interests}\label{interests}

\begin{itemize}
\tightlist
\item
  Reading, Writing, Podcasts, Music, Sports (football, rugby, cricket).
\item
  Played Rugby competitively for 8 years.
\item
  Member of the NTU Rugby Squad (Sept 2010 - Aug 2011).
\end{itemize}
